ABC Group Level Fits

### 2024-01-09 Model/abc_group.qmd
fix plot saving function

  ggsave(filename = here::here(density_filename), plot = density_plot, width = 10, height = 6)
  ggsave(filename = here::here(distance_filename), plot = distance_plot, width = 10, height = 6)
}

@@

# Save plots
#invisible(lapply(seq_along(names(datasets)), function(i) save_plots(density_plots[[i]], distance_plots[[i]], names(datasets)[i])))

>>>>

  ggsave(filename = here::here(density_filename), plot = density_plot, bg = "white", width = 10, height = 6)
  ggsave(filename = here::here(distance_filename), plot = distance_plot, bg = "white", width = 10, height = 6)
}

@@

# Save plots
invisible(lapply(seq_along(names(datasets)), function(i) save_plots(density_plots[[i]], distance_plots[[i]], names(datasets)[i])))

### 2024-01-09 Model/abc_hier.qmd
fix plot saving function

# group_prior=abc_1M_p001 = readRDS(here::here("data/abc_1M_rmse_p001.rds"))
group_prior=abc_2M_p001 = readRDS(here::here("data/abc_2M_rmse_p0001.rds"))
# names(group_prior)
# str(group_prior$abc_ev[[1]] |> select())

@@

# posterior distribution from fit to entire varied group
gp_teter_v <- teter |>  filter(Group=="Varied",Model=="ALM") |> select(c,lr)
head(gp_teter_v)

@@

fhat <- get_fhat(gp_teter_v$c, .1516)
curve(fhat, from=min(gp_teter_v$c), to=max(gp_teter_v$c))

fhat <- get_fhat(gp_teter_v$lr, .1516)
curve(fhat, from=min(gp_teter_v$lr), to=max(gp_teter_v$lr))

kde_result <- MASS::kde2d(gp_teter_v$c, gp_teter_v$lr, n = 10)
contour(kde_result)
image(kde_result)
persp(kde_result)

plot(density(kde_result$x))

ggplot(data.frame(x=kde_result$x), aes(x=x)) +
      geom_density()

ggplot(data.frame(x=gp_teter_v$c), aes(x=x)) +
      geom_density()

>>>>

# group_prior=abc_1M_p001 = readRDS(here::here("data/abc_1M_rmse_p001.rds"))
group_prior=abc_2M_p001 = readRDS(here::here("data/abc_2M_rmse_p001.rds"))
# names(group_prior)
# str(group_prior$abc_ev[[1]] |> select())

@@

# posterior distribution from fit to entire varied group
gp_teter_v <- teter |>  filter(Group=="Constant",Model=="Alt_EXAM") |> select(c,lr)
head(gp_teter_v)

@@

kde_result <- MASS::kde2d(gp_teter_v$c, gp_teter_v$lr, n = 50)
contour(kde_result)
image(kde_result)
persp(kde_result)

density_c <- apply(kde_result$z, 1, sum)
density_c <- density_c / sum(density_c)

density_lr <- apply(kde_result$z, 2, sum)
density_lr <- density_lr / sum(density_lr)

plot(kde_result$x, density_c, type = 'l', xlab = 'c', ylab = 'Density')
plot(kde_result$y, density_lr, type = 'l', xlab = 'lr', ylab = 'Density')

ggplot(data.frame(x=kde_result$y), aes(x=x)) +
      geom_density()

ggplot(data.frame(x=gp_teter_v$lr), aes(x=x)) +
      geom_density()
